Analysis

### 2018-06-28 reports/analysis_pilot.Rmd
add test
Finished testing of pilot data

# Visualize

```{r}
df %>% ggplot(aes(x = quintile, y = correct)) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  ylim(0,1)+
  theme(aspect.ratio = 1) +
  geom_hline(yintercept = 1/9) 
```

## Express the distances as ratio

@@

### And visualize

@@

@@

### Correlation between raters

>>>>

# Quintiles

## Visualize

```{r}
df %>% ggplot(aes(x = quintile, y = correct)) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  ylim(0,1)+
  theme(aspect.ratio = 1) +
  geom_hline(yintercept = 1/9)

df %>% ggplot(aes(x = quintile, y = correct)) + 
  stat_summary(fun.data = "mean_cl_boot") + 
  ylim(0,1)+
  theme(aspect.ratio = 1) +
  facet_wrap(~subject_id) +
  geom_hline(yintercept = 1/9) 
```

## Test

```{r lmer}
library(lme4)

glm1 <- glmer(cbind(correct,1-correct) ~ quintile + (1|subject_id) + (1|category), df, family = binomial())
glm1_null <- glmer(cbind(correct,1-correct) ~ (1|subject_id) + (1|category), df, family = binomial())
anova(glm1, glm_null)

# Express the distances as ratio

@@

## Visualize

@@

df %>% ggplot(aes(x = d_ratio, y = correct)) + 
  geom_point() +
  stat_smooth(method="glm", method.args = list(family = "binomial"), se=F) +
  ylim(0,1)+
  theme(aspect.ratio = 1) +
  geom_hline(yintercept = 1/9)

@@

## Test

```{r lmer}
library(lme4)

glm2 <- glmer(cbind(correct,1-correct) ~ d_ratio + (1|subject_id) + (1|category), df, family = binomial())
glm_null <- glmer(cbind(correct,1-correct) ~ (1|subject_id) + (1|category), df, family = binomial())
anova(glm2, glm_null)

# Correlation between raters
